Sr: Processing Data Streams By Doing Less Work

### 2012-05-03 paper/paper.tex
Remove extra space from the verbatim block
add all section headers
Add start of evaluation section and referencify table and figures

\usepackage{fullpage}

@@

@@

\section{Methodology}
The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers, 1 collector, and 1 master. Roles are partitioned among nodes as shown in figure 1. Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each. The master, spout, fetcher, and collector ran on my laptop, a mid-2010 Macbook Air with 4GB of RAM.

@@

\end{verbatim}
\caption{Topology of the test Sr cluster. Each box is a single machine.}
\end{figure}

@@

To serve the data, I munged it into a YAML file containing a hash of \texttt{article\_id => fulltext}. To store fulltext, I base64 encoded it and deflated it. This requires workers to inflate and decode the fulltext before they can process it further. The server reads from this YAML file and returns the resulting hash as JSON.

@@

Workers are initialized with the 3 computation routines shown in table 1.

\begin{center}
\begin{table}
\begin{tabular}{|l|p{5cm}|}
 \hline
Weight & Description \\ \hline
1.0 & Deflate and decode fulltext and count words in all of fulltext \\ \hline
0.25 & Deflate and decode fulltext and count words in approximately a quarter of fulltext \\ \hline
0.1 & Return the results of the last computation from a cache \\ \hline
\end{tabular}
\caption{Computation routines used by Sr workers}
\end{table}
\end{center}

>>>>

\usepackage{fullpage}
\usepackage{listings}
\usepackage{graphicx}
\graphicspath{{images/}}

@@

\section{Introduction}

\section{Related Work}

@@

\section{Methodology}
The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers, 1 collector, and 1 master. Roles are partitioned among nodes as shown in Figure ~\ref{fig:clusterDiagram}. Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each. The master, spout, fetcher, and collector ran on my laptop, a mid-2010 Macbook Air with 4GB of RAM.

@@

\end{verbatim}
\caption{Topology of the test Sr cluster. Each box is a single machine.}
\label{fig:clusterDiagram}
\end{figure}

@@

To serve the data, I munged it into a YAML file containing a hash of \lstinline[language=Ruby]{article_id : fulltext}. To store fulltext, I base64 encoded it and deflated it. This requires workers to inflate and decode the fulltext before they can process it further. The server reads from this YAML file and returns the resulting hash as JSON.

@@

Workers are initialized with the 3 computation routines shown in Table ~\ref{table:workerTasks}.

\begin{table}
\begin{tabular}{|l|p{5cm}|}
 \hline
Weight & Description \\ \hline
1.0 & Deflate and decode fulltext and count words in all of fulltext \\ \hline
0.25 & Deflate and decode fulltext and count words in approximately a quarter of fulltext \\ \hline
0.1 & Return the results of the last computation from a cache \\ \hline
\end{tabular}
\caption{Computation routines used by Sr workers}
\label{table:workerTasks}
\end{table}

The results of the word count job are then used in a script to compute the top 100 words. The cluster and word count job could be used in a two-stage top-k job. This script filters out SEO stopwords [stopword] to achieve more interesting results.

\section{Evaluation}
To evaluate Sr, I explore the speedup factor associated with varying the kill rate and target work level as well as the precision and recall of the word count test job.
\subsection{Speedup}
Sr is able to achieve a speedup over a MapReduce-style computation through three mechanisms: providing multiple computation routines for the workers to choose from; varying the task kill rate; and varying the target work level, which influences the chosen frequency of computation routines per worker.

Table ~\ref{table:runtime} shows the effect of varying the kill rate and work level. The row with kill rate = 0.0 and work level = 1.0 represents the perfect, “correct” execution of the word count job. The only consistent reduction in execution time is a result of increasing the kill rate. Increasing the kill rate exhibits a linear reduction in execution time as the fraction of processed data linearly decreases.

\begin{table}
\begin{tabular}{|l|l|l|}
\hline
Kill rate & Work level & Avg. execution time \\ \hline
0.0 & 1.0 & 11:35.5 \\ \hline
0.0 & 0.4 & 10:33.8 \\ \hline
0.0 & 0.8 & 10:30.8 \\ \hline
0.2 & 0.4 & 08:25.8 \\ \hline
0.2 & 0.8 & 08:37.8 \\ \hline
0.4 & 0.4 & 06:54.0 \\ \hline
0.4 & 0.8 & 06:28.2 \\ \hline
0.6 & 0.4 & 04:14.7 \\ \hline
0.6 & 0.8 & 04:13.7 \\ \hline
0.8 & 0.4 & 02:33.3 \\ \hline
0.8 & 0.8 & 02:15.0 \\ \hline
\end{tabular}
\caption{Impact of Kill rate and work level on job execution time}
\label{table:runtime}
\end{table}

\subsection{Precision and Recall}
In order for task killing to be an effective strategy for a top-k computation, the distribution of words in the corpus must be able to sustain data loss. This is the case if the distribution is long-tailed, but is not true if the distribution is uniform.

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{Frequencies of words in the Wikipedia Featured Articles corpus}
\label{fig:wordDist}
\end{figure}

The distribution shown in Figure ~\ref{fig:wordDist} is long-tailed, meaning that killing tasks will impact the tail of the distribution more than the head.

\subsubsection{Precision}
Task killing should least impact the head of the word distribution. Figure ~\ref{fig:precision} shows that even with a kill rate of 0.8 and a work level of 0.4, meaning that the cluster only looks at 8\% of the words in the corpus, the results are at least 80\% accurate. Increasing the work level, which increases the fidelity of results emitted by workers, also increases the fidelity of the top 100 results.

\begin{figure}
\includegraphics[width=\linewidth]{top-100-precision.png}
\caption{Precision of top 100 results} 
\label{fig:precision}
\end{figure}

\subsubsection{Test Accuracy}
Because I am running a top k job, I compute the $F_{0.5}$-score of the Sr results as opposed to the $F1$-score because I care more about precision of the top k than recall in the tail.

\section{Discussion}

\section{Conclusion}

\section{Acknowledgements}

\section{References}
